Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Updated the section about metrics

The most widely used score for evaluating text summarizations is Recall-Oriented Understudy for Gisting Evaluation (ROUGE) inroduced by Chin-Yew Lin in 2004\cite{lin-4}\cite{das-7}\cite{kishore-2}.

@@

The problem with these scores is that all of them measure the number of words that occur in both expected and actual summary. This can be useful for extractive summarization but makes little sense for abstractive, because the summary can be generated with completely new words.

For example, if the expeced summary is \textit{"The great paper"} and our model produces the summary \textit{"A wonderful article"}, ROUGE score will be $0$, even though the summary is perfect.

@@

We propose a metric that uses word embeddings to evaluate summaries based on their semmantic distance to the space of expected summaries.

Our assumption is that a good summary of a document contains words that are semantically close to the most important words in that document.

Let's denote an $n$-word summary as $S = (s_1, s_2, \dots, s_n)$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important words in the document. We define the norm of each word in the summary as its distance to the closest important word in the document

\[ ||x||_{EMB} = \operatorname*{min}_j ||s_i - c_j||_2 \]

Now the norm of a whole summary is the average of the norms of it words

\[ ||S||_{EMB} = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]

To choose which words are important we can use an algorithm of extractive text summarization. We will use \textbf{term frequency-inverse document frequency} (tf-idf) as a measure of importance because of its simplicity and importance (according to \cite{kumar-16}, tf-idf is one of the universally used terminologies in extractive summarization).

>>>>

The most widely used score for evaluating text summarizations is ROUGE (Recall-Oriented Understudy for Gisting Evaluation) inroduced by Chin-Yew Lin in 2004\cite{lin-4}\cite{kishore-2}.

@@

ROUGE works well for extractive text summarization. But if we need to evaluate the generated summary which contains different words from the ones that occured in paper, the score will always be small because, even though the new words can be close to the expected ones, two summaries don't overlap in terms of word equality.

For example, if the human-created summary is \textit{"The great paper"} and our model produces \textit{"A wonderful article"}, ROUGE score will be $0$, even though the summary is perfect.

@@

We propose a metric that uses word embeddings to evaluate summaries based on their semmantic distance to the space of good summaries. Our assumption is that a good summary of a document contains words that are semantically close to the most important words or n-grams in that document.

Let's denote an $n$-word summary as $S = (s_1, s_2, \dots, s_n)$ and let $c_1, c_2, \dots, c_k$ be the $k$ most important n-grams in the document. For each n-gram in the generated summary we calculate the embedding-based score as its distance to the closest important n-gram in the document.

\[ \text{EBM-N}(s_i) = \operatorname*{min}_j ||s_i - c_j||_2 \]

Now we define the score of the whole summary as the average score of its words

\[ \text{EBM-N}(S) = \frac1n \sum_{i=1}^n \operatorname*{min}_j ||s_i - c_j||_2 \]

This metric is in fact the continuous version of ROUGE-N. Instead of testing the equality of n-grams in the compared summaries we use the continuous measure of semmantic distance between those n-grams.

\subsubsection{Measuring word importance}
To choose which words are important we can use an algorithm of extractive text summarization. We will use \textbf{term frequency-inverse document frequency} (tf-idf) as a measure of importance because of its simplicity and importance (according to \cite{kumar-16}, tf-idf is one of the universally used terminologies in extractive summarization).
